An Accurate Model for SARS-CoV-2 pooled RT-PCR Test Errors

### 2021-03-22 comment.tex
Discussion

\section{Discussion}
We have presented a novel model for pooled tests. It is hard to
assess the validity of our model, since this would require
considerably more data than available in \cite{Salazar}. However, our
model is as simple as possible, given that the standard assumptions
are refuted. We have no doubt that further study of the assumptions
underlying pooling is due. Furthermore, adapting common group testing
algorithms \cite{Kim} to novel error models should be further
studied.

Our revised model has some implications for the practice of
pooling. For example, although Dorfman pooling improves testing
throughput, we have shown that low values of infection prevalence, or
low values of single test false-negative rates, increase
$\rel{ours}$. These results remain qualitatively similar under varying
parameter values, in the observed ranges
\cite{KitComparison,EstimatingRatesKucrika, EstimatingRatesLourenco,
  InterpretingCOVID19Test} (Figure \ref{figy}).

>>>>

\section{Discussion}
This is my suggestion for a Discussion structure:
short recap; implications for group testing in different prevalence settings; limitations; ways to reduce errors (*cough* DOPE); conclusion/take home message

We have presented a novel model for pooled tests. It is hard to
assess the validity of our model, since this would require
considerably more data than available in \cite{Salazar}. However, our
model is as simple as possible, given that the standard assumptions
are refuted. We have no doubt that further study of the assumptions
underlying pooling is due. Furthermore, adapting common group testing
algorithms \cite{Kim} to novel error models should be further
studied.

Our results have practical implications for the use of
pooling schemes. As the COVID-19 pandemic progresses, the infection prevalence in various tested populations undergoes frequent changes. Hence, as our results suggest, pooling strategies for mass testing should be used with caution in populations where infection rates are low. Such mass-tested populations often include air travel passengers, potentially importing infections, or asymptomatic individuals, such as children,  and can be crucial for controlling outbreaks(ref)

For example, although Dorfman pooling improves testing
throughput, we have shown that low values of infection prevalence, or
low values of single test false-negative rates, increase
$\rel{ours}$. These results remain qualitatively similar under varying
parameter values, in the observed ranges
\cite{KitComparison,EstimatingRatesKucrika, EstimatingRatesLourenco,
  InterpretingCOVID19Test} (Figure \ref{figy}). Hence,
